---
title: "Graphiques communs"
author: "Clovis"
date: '13_05_22'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include=FALSE}
library(tidyverse)
library(nycflights13)
```

Voici les différents graphiques que le groupe OPEN22 a produit :

```


# Graphique CB :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_CB.R")
```

# Graphique LD :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_LD.R")
```

# Graphique JH :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_JH.R")
```

# Graphique GK :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_GK.R")
```

# Graphique ML

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_ML.R")
```
# Graphique CL :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_CL.R")
```
# Graphique PP :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_PP.R")
```
# Graphique LS :

```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_LS.R")
```
# Graphique HV :
```{r Graphique_CB, echo = FALSE, eval = TRUE}
source("source/Graphique_HV.R")
```



 




 
 
